%preamble
\documentclass[10pt,a4paper,hidelinks]{moderncv}
\moderncvcolor{red}
\moderncvstyle{classic}
\usepackage[a4paper,margin=0.85in,scale=0.75]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\recomputelengths
\nopagenumbers{}

%preamble - Head and footer
\colorlet{lastnamecolor}{gray}
\colorlet{firstnamecolor}{gray}
\colorlet{namecolor}{lastnamecolor}

%preamble - title info
\firstname{Kejvin}
\familyname{Xhakaj}
\title{Software Engineer}
\mobile{+355685103050}
\social[linkedin]{linkedin.com/in/kejvin}
\social[github]{github.com/kevin-xhk}
\email{kevinxhakaj@gmail.com}

\begin{document}

\maketitle

\hfill

% -------------------- Education --------------------

\section{Education}
	\cventry{Oct 2018 - Jun 2022}{Bachelor of Science in Computer Science}{Empire State College}{NY, USA}{}{Dual Degree Program, Final Grade: 3.50 / 4.00}
	\cventry{Oct 2020 - Jun 2022}{Bachelor in Computer Science}{University of New York Tirana}{Tirana}{}{Dual Degree Program, Final Grade: 3.66 / 4.00}
\closesection{}

\hfill


% -------------------- Experience --------------------

\section{Experience}
	\cventry{April 2024 - cont.}{Analyst - Salesforce Developer}{Balance Albania / Exprivia}{}{}{Tirana, Albania}
		\cvlistitem{Continued my efforts in developing and improving the experience of users in Service and Experience Cloud}
		\cvlistitem{Worked and delivered on critical features for big clients in a project with a large team by following the Waterfall structure.}
		\cvlistitem{Digitalized and automated processes that clients use daily for handling thousands of customer complaints and claims on tangible issues, like public illumination.}
	\cventry{Jun 2022 - Feb 2024}{Consultant - Salesforce Developer}{Deloitte Digital CE}{}{}{Tirana, Albania}
		\cvlistitem{Analysed, Designed and Implemented Salesforce solutions to customers from Test to Production in Sales, Service and Experience Cloud}
		\cvlistitem{Worked on different aspects of the project's lifecycle while collaborating with a tight team in an agile environment}
		\cvlistitem{Delivered features that improved the experience of hundreds of operators, who serve even more Businesses on the Salesforce platform}
\closesection{}

\hfill


% -------------------- Projects --------------------

\section{Projects}
	\cventry{Apr 2024 - cont.}{ACEA - Areti}{Salesforce Developer}{}{}{Balance Albania}
		\cvlistitem{Worked with a diverse team on a very active and healthy \textbf{Service and Experience Cloud} project for the biggest electricity distribution company in Rome, Italy.}
		\cvlistitem{Collaborated with a wide range of parallel, integrated teams that made possible Salesforce's integration with services like secured archival of files, automated document generation and management of administrative procedures (\textbf{Pratiche}) in order to aid Service Operators in providing the best possible service to customers of all kinds: Private, Businesses and Energy Producers.}
		\cvlistitem{Automated the creation and ease of operation of Customer Claims (\textbf{Reclami}), where \textbf{thousands} of customer issues ranging from public illumination, points of devilery and related issues are solved every single day. }
		\cvlistitem{Delievered features that implement the most bleeding edge technology to level up the day-to-day operations of Service Operators. Examples include Einstein AI Classification of cases, AI text-generation for documents used in official responses to clients, Chatbots, Skill-based Omnichannel routing, and much more. }
	\hfill
\closesection{}

\newpage

\section{Projects (cont.)}
	\cventry{Jun 2023 - Feb 2024}{GES Service Cloud}{Salesforce Developer}{}{}{Deloitte Digital}
		\cvlistitem{Followed the software development lifecycle through all its steps in order to quickly deliver \textbf{Apex and Lightning Web Components} solutions}
		\cvlistitem{Developed and replaced the legacy email-to-case with a new \textbf{scalable} system that creates multiple Support Tickets from a single support email, greatly improving the case management experience of hundreds of important Business Customers}
		\cvlistitem{Designed, Developed and Delivered a feature-rich custom email composer well integrated with Salesforce in order to enhance support-to-client communications.}
	\hfill
	\cventry{Jan 2023 - May 2023}{IoT Salesforce Integration}{Python Developer}{}{}{Deloitte Digital}
		\cvlistitem{Python script to act on temperature readings captured from sensors of industry pumps connected to an on-site Raspberry Pi.}
		\cvlistitem{\textbf{Integrated} such solution with Salesforce to send platform events in the case of the detection of critical temperatures.}
		\cvlistitem{Provided the support team with \textbf{real-time} alerts of abnormal pump temperatures, greatly improving the team's efficiency during crises.}
	\hfill
	\cventry{Apr 2022 - June 2022}{GoodBooks}{Backend Developer}{}{}{Empire State College}
		\cvlistitem{Book Library Tracking Webapp built with Spring / Spring Security (Kotlin)}
		\cvlistitem{Implemented authentication through \textbf{Spring Security}, MySQL database for storing user book selections, ratings, and reviews, presented in plain JS. Implemented REST API services for the front and back end. Book data retrieved through Open Library API.}
	\hfill
	\cventry{May 2021}{SoundTrack}{Backend - Frontend Developer}{}{}{University of New York Tirana}
		\cvlistitem{Native Android app to track music albums and artists.}
		\cvlistitem{built with Android SDK in \textbf{Java}, authentication, and storage \textbf{Firebase}. Data received through the Music Brainz API.}
	\hfill
\closesection{}

\hfill


% -------------------- Technical Skills --------------------

\section{Technical Skills}
	\begin{itemize}
		\item \textbf{Proficient:} Java, Kotlin, Apex, Salesforce, Flows, Git.
		\item \textbf{Conversational:} Spring Framework, Python, Javascript, Lightning Web Components, Azure DevOps.
	\end{itemize}
\closesection{}

\hfill


% -------------------- Languages --------------------

\section{Languages}
	\cvdoubleitem{\textbf{Italian}}{Native}{\textbf{Albanian}}{Native}
	\cvdoubleitem{\textbf{English}}{C1 - BSc, IELTS (7.5)}{\textbf{Japanese}}{JLPT N4 - Self-Learning}
\closesection{}

\hfill


% -------------------- Certifications --------------------

\section{Certifications}
	\cventry{Aug 2024}{Certified Platform Administrator}{Salesforce}{}{}{}
	\cventry{Feb 2023}{Certified CPQ Administrator}{Salesforce}{}{}{}
	\cventry{Oct 2022}{Certified Omnistudio Developer}{Salesforce}{}{}{}
	\cventry{Nov 2022}{Certified Platform Developer}{Salesforce}{}{}{}
\closesection{}

\hfill


% -------------------- Personal --------------------

\section{Personal}
As an agile \textbf{Salesforce Developer} with an itch for \textbf{Kotlin} and efficiency, I'm always eager to learn more and nurture my professional career by going head-first into whatever comes my way. I'm not afraid to wear many hats, as I have invested my time in a plethora of related fields. I enjoy running and  have recently started collecting vinyls.
\closesection{}

\end{document}